%The buildings of our science fiction dreams have always adapted to the needs of their occupants.
%Today, "smart buildings" are poised to become reality, enabled by advances in sensors that monitor room-level occupancy and movement.
Reliable and accurate room-level occupancy-tracking systems can enable many new advances in sensors and applications of modern smart buildings.
This allows buildings to be more capable of adapting to the needs of their occupants in their day-to-day activities and better optimize certain resources, such as power and air conditioning, to do so.
Unfortunately, existing occupancy-tracking systems are plagued by large size, high energy consumption, and, unsurprisingly, short battery lifetimes.

In this paper, we present \sysname, a \textit{batteryless}, room-level occupancy monitoring sensor that harvests energy from indoor ambient light reflections, and uses changes in these reflections to detect when people enter and exit a room.
%This information is then communicated by radio to a basestation for further processing and actuation.
\sysname is mountable at the top of a doorframe, allowing for detection of a person and the direction they are traveling at the entry and exit point of a room.
We evaluated the \sysname sensor in an office-style setting under mixed lighting conditions (natural and artificial) on both sides of the doorway with subjects exhibiting varying physical characteristics such as height, hair color, gait, and clothing.
\numExp number of controlled experiments were ran on \numDoors doorways with \numPeople individuals and achieved a total detection accuracy of \SysAccuracy.
Further, it judged the direction of movement correctly with an accuracy of \dirAccuracy.
This paper also evaluates and discusses various practical factors that can impact the performance of the current system in actual deployments.
%While challenges remain, t

This work demonstrates that ambient light reflections provide both a promising low-cost, long-term sustainable option for monitoring how people use buildings and an exciting new research direction for \textit{batteryless} computing.
